### 2018-05-04 manuscript/relatedwork.tex
manuscript updated

\paragraph{Map Distrotion}

\paragraph{Facility Accessibility Analysis}

>>>>

\textbf{Anonymous Movement Analysis} Introduce the classifical movement analysis focus. Data mining (Zheng Yu's work), Specially in the field of visual analytics, also most of work focus on the efficiency of the travel infrustions, (Wang, Lu, Zeng, Qu, Wu Yingcai).

\textbf{Social Related Analysis} In the GIS field, (Liu Yu), Soical Media (Chen, CaoNan)
